What Does Reproducible Research Mean for Plant Pathology?

### 2016-12-11 What Does Reproducible Research Mean for Plant Pathology.Rmd
Correct R citation on line 62
Added example of reproducible report

---
title: "What Does Reproducible Research Mean for Plant Pathology?"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
bibliography: bibliography.bib
csl: phytopathology.csl
---

@@

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects
of climate change on potato late blight.
* Other examples from plant pathology providing e-Xtras or supplemental material

@@

The list of journals was saved as a comma separated value (CSV) file and imported into R (R2016).

>>>>

---
title: "What Does Reproducible Research Mean for Plant Pathology?"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: '`r Sys.Date()`'
output:
  word_document:
    keep_md: yes
    reference_docx: Phytopathology_Style_Reference.docx
  html_document: default
csl: phytopathology.csl
bibliography: bibliography.bib
---

@@

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
* Other examples from plant pathology providing e-Xtras or supplemental material

@@

The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2016].
